Drones in Wind

### 2017-08-16 Papers/DroneInTheWind.tex
Update DroneInTheWind.tex
paper updates

% Say where pictures (if any) will be placed
\graphicspath{{./pictures/}}

@@

\begin{equation}
\label{B_matrix_intermediate}
B = \begin{bmatrix} 0 && 0 \\ 0 && \frac{\sin{\theta}}{m} \\ 0 && 0 \\ 0 && \frac{\cos{\theta}}{m} \\ 1 && 0 \end{bmatrix}
\end{equation}
Substituting the equilibrium force, $f = mg$, results in the following matrices shown in Equation \ref{A_matrix} and Equation \ref{B_matrix}.
\begin{equation}
\label{A_matrix}
A = \begin{bmatrix} 0 && 1 && 0 && 0 && 0 \\ 0 && 0 && 0 && 0 && g\cos{\theta} \\  0 && 0 && 0 && 1 && 0 \\ 0 && 0 && 0 && 0 && -g\sin{\theta} \\ 0 && 0 && 0 && 0 && 0 \end{bmatrix}
\end{equation}

\begin{equation}
\label{B_matrix}
B = \begin{bmatrix} 0 && 0 \\ 0 && \frac{\sin{\theta}}{m} \\ 0 && 0 \\ 0 && \frac{\cos{\theta}}{m} \\ 1 && 0 \end{bmatrix}
\end{equation}

@@

OptimTraj \cite{OptimTraj} was used for trajectory planning. OptiTraj is a MATLAB library designed by a Cornell PHD student, Matthew P. Kelly, to solve for continuous-time single-phase trajectory optimization problems. For OptimTraj to solve the optimal trajectory, you must specify various parameters of your problem, including:
\begin{itemize}
  \item Dynamics
  \item Objective function
  \item Bounds
  \item Initial trajectory guesses
\end{itemize}

@@

\begin{figure}[H]
\begin{equation*}
\lstinline!problem.guess.time! = [t_{i}, t_{f}]
\end{equation*}
\begin{equation*}
\lstinline!problem.guess.state! = [x_{i}, x_{f}]
\end{equation*}
\begin{equation*}
\lstinline!problem.guess.control! = [u_{i}, u_{f}] 
\end{equation*}
\end{figure}
\subsubsection{Options}
Additional options are available using \lstinline!problem.options!, which include details to change accuracy settings and select different solution methods, like trapezoid, Chebyshev, etc.
\subsubsection{Solution}
Finally, running the command \lstinline!soln = optimTraj(problem)! is used to solve. Following this, it is possible to unpack the simulation, save the data, and plot out.
\begin{quote}
\begin{lstlisting}
t = linspace(soln.grid.time(1),soln.grid.time(end),soln.grid.time(end)*TimeDensity);
x = soln.interp.state(t);
u = soln.interp.control(t);
save('traj.mat','t','x','u');
\end{lstlisting}
\end{quote}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%                                                                               Controller                                                                              %
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\subsection{Controller}
The controller is designed to use in the loop control with LQR to follow a given trajectory. First, the init function creates a symbolic description of the A and B matrices, in which the angle $\theta$ is the only variable.  These symbolic descriptions are then turned into MATLAB functions and saved in the data struct.  The Q and R weight matrices are then initialized.  The init function proceeds to load in the trajectory data and also adds it to the data struct.  Finally, some parameters used to determine when the quad has reached its destination are initialized.
\begin{quote}
\begin{lstlisting}
% Create functions
data.funcA = matlabFunction(A);
data.funcB = matlabFunction(B);

@@

Logic is used at the start of the control loop to determine if there is still trajectory data available for the current timestep.  If there is not, the controller will linearize about the last available trajectory point.  This case does not happen in current simulations because the trajectory is planned for the entire duration of the simulation.
\begin{quote}
\begin{lstlisting}
% Create functions
if data.index <= length(data.T)
    data.x_eq = [data.X(data.index);
                 data.Xdot(data.index);
                 data.Z(data.index);
                 data.Zdot(data.index);
                 data.Theta(data.index)];

@@

\end{lstlisting}
\end{quote}
Where \lstinline!data.index! is initialized at 1. 
\newline
\newline
After determining that the simulation is still within the regime in which a trajectory is available, the controller will find the respective trajectory point to linearize about for the current time-step.  The angle for this trajectory point is passed into the MATLAB functions to determine the relevant A and B matrices, which are then used in conjunction with the already initialized weights to create a gain matrix using LQR.
\begin{quote}
\begin{lstlisting}
theta = data.x_eq(5,1);
A = data.funcA(theta);
B = data.funcB(theta);

@@

Finally, the input $u = -Kx$ is applied in which $u$ is a column of two inputs, the first being thrust and the second being pitch rate.  Note here that for hover, the thrust \textit{must} augmented by the equilibrium condition, $f = mg$.  K is the previously specified gain matrix, and x is the difference between the current state and the trajectory state at the current time.

@@

To run the simulation, a function named \lstinline!automation.m! was used to set up the problem bounds, plan the optimal trajectory, and analyze the results. Below is shown the script to do so.
\begin{quote}
\begin{lstlisting}
% Constants to be applied
clear;

@@

\begin{figure}[h!]
  \centering
  \begin{minipage}[b]{0.5\textwidth}
    \includegraphics[width=\textwidth]{State.png}
    \caption{\label{State Plot} Quadcopter state over time.}
  \end{minipage}
  \hfill
  \begin{minipage}[b]{0.45\textwidth}
    \includegraphics[width=\textwidth]{Inputs.png}
    \caption{\label{Input Plot} Quadcopter Inputs over time.}
  \end{minipage}
\end{figure}

@@

Though both results are nearly identical, the biggest difference in performance is in that of the inputs. 
D'Andrea input for thrust is bang-bang, meaning there is a switch discontinuity AND the input only takes the minimum and maximum values \cite{BangBangControl}. D'Andrea's pitch rate is bang-singular, meaning the control input is always at full positive or negative saturation, except during singular arcs \cite{D'Andrea}.

In our model, the inputs were free to vary as continuously as possible between the bounds set in table \ref{Problem Bounds}. Despite this, both models arrived at the destination $x=z=5$ following the same time-optimal path and input behavior.

>>>>

% Say where pictures (if any) will be placed
\graphicspath{{./Pictures/}}

@@

	\begin{equation}
	\label{B_matrix_intermediate}
	B = \begin{bmatrix} 0 && 0 \\ 0 && \frac{\sin{\theta}}{m} \\ 0 && 0 \\ 0 && \frac{\cos{\theta}}{m} \\ 1 && 0 \end{bmatrix}
	\end{equation}
	There is no need to substitute in equilibrium conditions because we will be linearizing about a trajectory.

@@

	OptimTraj \cite{OptimTraj} was used for trajectory planning. OptimTraj is a MATLAB library designed by a Cornell PHD student, Matthew P. Kelly, to solve for continuous-time single-phase trajectory optimization problems. For OptimTraj to solve the optimal trajectory, you must specify various parameters of your problem, including:
	\begin{itemize}
		\item Dynamics
		\item Objective function
		\item Bounds
		\item Initial trajectory guesses
	\end{itemize}

@@

	\begin{figure}[H]
		\begin{equation*}
		\lstinline!problem.guess.time! = [t_{i}, t_{f}]
		\end{equation*}
		\begin{equation*}
		\lstinline!problem.guess.state! = [x_{i}, x_{f}]
		\end{equation*}
		\begin{equation*}
		\lstinline!problem.guess.control! = [u_{i}, u_{f}] 
		\end{equation*}
	\end{figure}
	\subsubsection{Options}
	Additional options are available using \lstinline!problem.options!, which include details to change accuracy settings and select different solution methods, like trapezoid, Chebyshev, etc.
	\subsubsection{Solution}
	Finally, running the command \lstinline!soln = optimTraj(problem)! is used to solve. Following this, it is possible to unpack the simulation, save the data, and plot it.
	\begin{quote}
		\begin{lstlisting}
		t = linspace(soln.grid.time(1),soln.grid.time(end),soln.grid.time(end)*TimeDensity);
		x = soln.interp.state(t);
		u = soln.interp.control(t);
		save('traj.mat','t','x','u');
		\end{lstlisting}
	\end{quote}

@@

	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	%                                                                               Controller                                                                              %
	%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
	\subsection{Controller}
	The controller is designed to use in the loop control with LQR to follow a given trajectory. First, the init function creates a symbolic description of the A and B matrices, in which the angle $\theta$ and the thrust $f$ are the only variables.  These symbolic descriptions are then turned into MATLAB functions and saved in the data struct.  The Q and R weight matrices are then initialized.  The init function proceeds to load in the trajectory data and also adds it to the data struct.  Finally, some parameters used to determine when the quad has reached its destination are initialized.
	\begin{quote}
		\begin{lstlisting}
		% Create functions
		data.funcA = matlabFunction(A);
		data.funcB = matlabFunction(B);

@@

	Logic is used at the start of the control loop to determine if there is still trajectory data available for the current timestep.  If there is not, the controller will linearize about the last available trajectory point.
	\begin{quote}
		\begin{lstlisting}
		% Create functions
		if data.index <= length(data.T)
		data.x_eq = [data.X(data.index);
		data.Xdot(data.index);
		data.Z(data.index);
		data.Zdot(data.index);
		data.Theta(data.index)];

@@

		\end{lstlisting}
	\end{quote}
	Where \lstinline!data.index! is initialized at 1. 
	\newline
	\newline
	After determining that the simulation is still within the regime in which a trajectory is available, the controller will find the respective trajectory point to linearize about for the current time-step.  The angle and thrust for this trajectory point is passed into the MATLAB functions to determine the relevant A and B matrices, which are then used in conjunction with the already initialized weights to create a gain matrix using LQR.
	\begin{quote}
		\begin{lstlisting}
		theta = data.x_eq(5,1);
		A = data.funcA(theta);
		B = data.funcB(theta);

@@

	Finally, the input $u = -Kx + n$ is applied in which $K$ is the previously specified gain matrix, $x$ is the difference between the current state and the trajectory state at the current time, and $n$ is the trajectory input at the current time.

@@

	To run the simulation, a function named \lstinline!automation.m! was used to set up the problem bounds, plan the optimal trajectory, and analyze the results. Shown below is the script to do so.
	\begin{quote}
		\begin{lstlisting}
		% Constants to be applied
		clear;

@@

	\begin{figure}[h!]
		\centering
		\begin{minipage}[b]{0.49\textwidth}
			\includegraphics[width=\textwidth]{State.png}
			\caption{\label{State Plot} Quadcopter state over time.}
		\end{minipage}
		\hfill
		\begin{minipage}[b]{0.49\textwidth}
			\includegraphics[width=\textwidth]{Inputs.png}
			\caption{\label{Input Plot} Quadcopter Inputs over time.}
		\end{minipage}
	\end{figure}

@@

	Though both results are nearly identical, the biggest difference in performance is in that of the inputs. 
	D'Andrea input for thrust is bang-bang, meaning there is a switch discontinuity and the input only takes the minimum and maximum values \cite{BangBangControl}. D'Andrea's pitch rate is bang-singular, meaning the control input is always at full positive or negative saturation, except during singular arcs \cite{D'Andrea}.

	In our model, the inputs were free to vary as continuously as possible between the bounds set in table \ref{Problem Bounds}. Despite this, both models arrived at the destination $x=z=5$ following approximately the same time-optimal path and input behavior.
